Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})

### 2019-08-21 manuscript/pest-management-science/main.tex
updated manuscript title
added figures to manuscript

\title{title}

@@

>>>>

\title{Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})}

@@

\paragraph{Population Monitoring}

\paragraph{Onion Maggot Mortality}

\paragraph{Field Damage}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-1.pdf}
\caption{Population dynamics of adult onion maggot (\textit{D. antiqua} flies in upstate New York muck regions.  Points indicate observations of numbers of adult flies captured on sticky cards.  Lines and shaded regions indicate smoothed fits and 95\% confidence intervals respectively.  }
\label{fig:figure1}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-2.pdf}
\caption{Adult onion maggot (\textit{D. antiqua} mortality in the presence of spinosad treated spheres.  (A) Raw data of effects of exposure time and spinosad rate on mortality of adult onion maggot flies.  Light points indicate individual observations.  Solid points and error bars denote mean and 95\% confidence intervals respectively.  (B) Main effects of spinosad rate on adult onion maggot mortality.  Points and error bars denote mean effect and 95\% confidence intervals respectively.  (C) Main effect of exposure time on adult onion maggot mortality.  Line and shaded area denote effect and 95\% confidence region respectively.  (D) Photographs of spinosad treated spheres at increasing exposure time in field conditions.  Spheres were placed in the field on the 15th of May.  }
\label{fig:figure2}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-3.pdf}
\caption{Adult onion maggot fly mortality following introduction to cages containing spinosad treated spheres.  Spheres were treated with differing rates of spinosad (rows) and exposed to field conditions for increasing amounts of time (column).  Lines and shaded regions indicate fitted smoothed (LOESS) mortality rates and 95\% confidence regions respectivel.  }
\label{fig:figure3}
\end{figure}

\begin{figure}[bt]
\centering
\includegraphics[width = 8cm]{figures/final-figures/figure-4.pdf}
\caption{Field damage of onions.  (A) End of season stand loss of onions (number of dead onion maggot plants) as a result of all mortality factors.  (B) Cumulative damage (number of dead onion maggot plants) as a result of onion maggot larval feeding.  Light points indicate observed values.  Solid points and errorbars denote mean effects and 95\% confidence intevals respectively.   }
\label{fig:figure4}
\end{figure}
